Running an open experiment: transparency and reproducibility in soil and ecosystem

### 2016-02-09 manuscript/cpcrw_manuscript.Rmd
Manuscript tweaks

The incubation experiment concluded on 9 December 2015, following the final CO~2~ and CH~4~ readings. Each soil core was maintained at the treatment-dependent temperature and moisture content (by mass) until removed for destructive sampling, December 14-18, 2015. Sub-samples were collected and composited throughout each soil core for dissolved organic carbon analysis (110 ± 24 g dry mass equivalent) and dry-mass calculations (~28 g each). The remaining core material was air-dried and separated into particles (>2 mm diameter) and soil (<2 mm) using a U.S. Standard Test Sieve No. 10 (Fisherbrand,  Pittsburg, PA, USA). The dry mass and volume of soil were used in calculations of gravimetric and volumetric soil moisture content, respectively {Gardner, 1986 #4345}. Soil volume was caclulated as the total core volume minus the volume of particles >2 mm diameter, with the latter determined by water displacement. Air-dried soil and sub-samples stored at -20 °C were sent to the Agricultural and Environmental Services Laboratory at the University of Georgia Extension in February 2016 for total C, N, and dissolved organic C. TODO: get UGA analytical methods.

>>>>

The incubation experiment concluded on 9 December 2015, following the final CO~2~ and CH~4~ readings. Each soil core was maintained at the treatment-dependent temperature and moisture content (by mass) until removed for destructive sampling, December 14-18, 2015. Sub-samples were collected and composited throughout each soil core for dissolved organic carbon analysis (110 ± 24 g dry mass equivalent) and dry-mass calculations (~28 g each). The remaining core material was air-dried and separated into particles (≥2 mm diameter) and soil (<2 mm) using a U.S. Standard Test Sieve No. 10 (Fisherbrand,  Pittsburg, PA, USA). The dry mass and volume of soil were used in calculations of gravimetric and volumetric soil moisture content, respectively {Gardner, 1986 #4345}. Soil volume was caclulated as the total core volume minus the volume of particles ≥2 mm diameter, with the latter determined by water displacement. Air-dried soil and sub-samples stored at -20 °C were sent to the Agricultural and Environmental Services Laboratory at the University of Georgia Extension in February 2016 for total C, N, and dissolved organic C. TODO: get UGA analytical methods.

### 2016-02-09 manuscript_openexperiment/Open_experiment.Rmd
Manuscript tweaks

---
title: 'Running an open experiment: transparency and reproducibility in soil and ecosystem
  science'
author: "Ben Bond-Lamberty, Peyton Smith, and Vanessa Bailey"
date: "February 2, 2016"
output: html_document
---

>>>>

---
title: 'Running an open experiment: transparency and reproducibility in soil and ecosystem
  science'
author: "Ben Bond-Lamberty^1^, Peyton Smith^2^, Vanessa Bailey^2^"
date: "February 2, 2016"
output: html_document
---
^1^Joint Global Change Research Institute, DOE Pacific Northwest National Laboratory, College Park, MD USA; 
bondlamberty@pnnl.gov

^2^Biological Sciences Division, Pacific Northwest National Laboratory, Richland, WA USA
